Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-10-20 analysis/paper/paper.Rmd
Revert "Remove "Rope Percentage" from table"
This reverts commit a7c2c1803f5d6bfa3685daa81cef8a1b6f57b5e3.

Conflicts:
	analysis/paper/supplementary_materials.Rmd

## Examples and Efforts from Related Disciplines

@@

@@

a_y_labs <- rev(gsub("b_abbreviation", "", parameters(m_f1)$Parameter)[-c(1:2)])
a <- plot(parameters(m_f1)) +
  scale_y_discrete(labels = a_y_labs) +
  scale_colour_grey() +
  ggtitle("Code")

b <- plot(parameters(m_f2)) +
  scale_colour_grey() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank()
  ) +
  ggtitle("Data")

@@

```{r year-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the year of publication for (A) computational materials (code) and (B) data being made readily available to the public. A test for practical equivalence indicated that there was no effect of year of publication on computational materials (code) being shared. A test for practical equivalence was undecided in finding effect of year of publication on supporting data being shared. Intervals in black indicate that the median value is above zero or more likely to share data and code indicating that as the year of publication increases, the likelyhood of sharing code or data may increase.', cache=FALSE, fig.env='figure'}
a <- plot(parameters(m_g1), show_labels = TRUE) + 
  scale_colour_grey() +
  ggtitle("Code")

b <- plot(parameters(m_g2), show_labels = TRUE) + 
  scale_colour_grey() +
   theme(
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank(),
      axis.title.y = element_blank()
    ) +
  ggtitle("Data")

@@

```{r IF-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the publishing journal\'s five-year impact factor for (A) computational materials (code) and (B) data being made readily available to the public. A test for practical equivalence was undecided on any detectable effects of impact factor. Intervals in black indicate that the median value is above zero or more likely to share data and code indicating that as the impact factor of the publication increases, the likelyhood of sharing code or data may increase', cache=FALSE, fig.env='figure'}
a <- plot(parameters(m_h1), show_labels = TRUE) + 
  scale_colour_grey() +
  ggtitle("Code")

b <- plot(parameters(m_h2), show_labels = TRUE) + 
  scale_colour_grey() +
   theme(
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank(),
      axis.title.y = element_blank()
    ) +
  ggtitle("Data")

>>>>

## Examples and Efforts from Other Disciplines

@@

@Seibold2021 investigated the types of methods and software used in PLOS ONE articles and whether the were able to reproduce the data analysis using open source software for papers that dealt with longitudinal data and used mixed effect models or generalized estimating equations for analysis and provided the data.
They found that most articles provided tables and visualisations only.
However, unlike our analysis, even with the data being supplied they found that only one article used open source software, whereas R prominently featured in the articles we examined along with other free open-source software packages.
Not surprisingly they found that replication was mostly difficult and required the results to be reverse engineered or contacting the authors.
They were unable to reproduce the results for for three articles and only parts of another two.
They needed to contact the articles' authors for all articles save two.
Their main conclusion was that reproducing papers is difficult if no code is provided and puts an undue burden on those interested in reproducing the work.

@@

a_y_labs <- rev(gsub("b_abbreviation", "", parameters(m_f1)$Parameter)[-c(1:2)])
a <- plot(equivalence_test(m_f1)) +
  scale_y_discrete(labels = a_y_labs) +
  scale_fill_grey() +
  ggtitle("Code")

b <- plot(equivalence_test(m_f2)) +
  scale_fill_grey() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank()
  ) +
  ggtitle("Data")

@@

```{r year-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the year of publication for (A) computational materials (code) and (B) data being made readily available to the public. A test for practical equivalence indicated that there was no effect of year of publication on computational materials (code) being shared. A test for practical equivalence was undecided in finding effect of year of publication on supporting data being shared. Intervals in black indicate that the median value is above zero or more likely to share data and code indicating that as the year of publication increases, the likelyhood of sharing code or data may increase.', cache=FALSE, fig.env='figure'}
a <- plot(equivalence_test(m_g1), show_labels = TRUE) + 
  scale_colour_grey() +
  ggtitle("Code")

b <- plot(equivalence_test(m_g2), show_labels = TRUE) + 
  scale_colour_grey() +
   theme(
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank(),
      axis.title.y = element_blank()
    ) +
  ggtitle("Data")

@@

```{r IF-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the publishing journal\'s five-year impact factor for (A) computational materials (code) and (B) data being made readily available to the public. A test for practical equivalence was undecided on any detectable effects of impact factor. Intervals in black indicate that the median value is above zero or more likely to share data and code indicating that as the impact factor of the publication increases, the likelyhood of sharing code or data may increase', cache=FALSE, fig.env='figure'}
a <- plot(equivalence_test(m_h1), show_labels = TRUE) + 
  scale_colour_grey() +
  ggtitle("Code")

b <- plot(equivalence_test(m_h2), show_labels = TRUE) + 
  scale_colour_grey() +
   theme(
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank(),
      axis.title.y = element_blank()
    ) +
  ggtitle("Data")
